A comparison of design-based and model-based approaches for spatial data.

### 2021-08-06 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
added mae.

dep_only <- combo_data_grts %>% filter(error_dep == "deperr")
dep_long <- dep_only %>%
  pivot_wider(names_from = approach, values_from = rmspe, sim) %>%
  mutate(perc = 100 * (`Design GRTS` - `Model GRTS`) / `Model GRTS`)
```

@@

```{r}
ggplot(data = dep_long, aes(x = fct_reorder(sim, perc), y = perc)) +
  geom_point() +
  coord_flip() +
  labs(y = "Percent Change in rmspe (Design - Model) / Model",
       caption = "Percent > 0 means Model has better rmspe")
```

@@

```{r}
design_better <- dep_long %>% filter(perc < -5)
design_better_full <- inner_join(combo_data_grts, design_better, by = c("sim"))
ggplot(data = design_better_full, aes(x = sim, y = coverage, colour = approach)) +
  geom_point() +
  coord_flip() +
  geom_hline(aes(yintercept = 0.95), alpha = 0.5)
```

>>>>

dep_only <- combo_data_grts %>% filter(error_dep == "deperr")
dep_long <- dep_only %>%
  pivot_wider(names_from = approach, values_from = rmspe, sim) %>%
  mutate(perc = 100 * (`Design GRTS` - `Model GRTS`) / `Model GRTS`)

dep_long_abs <- dep_only %>%
  pivot_wider(names_from = approach, values_from = medae, sim) %>%
  mutate(perc = 100 * (`Design GRTS` - `Model GRTS`) / `Model GRTS`)
```

@@

```{r}
ggplot(data = dep_long_abs, aes(x = fct_reorder(sim, perc), y = perc)) +
  geom_point() +
  coord_flip() +
  labs(y = "Percent Change in medae (Design - Model) / Model",
       caption = "Percent > 0 means Model has better rmspe")

ggplot(data = dep_long, aes(x = fct_reorder(sim, perc), y = perc)) +
  geom_point() +
  coord_flip() +
  labs(y = "Percent Change in rmspe (Design - Model) / Model",
       caption = "Percent > 0 means Model has better rmspe")
```

@@

```{r}
design_better <- dep_long %>% dplyr::filter(perc < -5)
design_better_full <- inner_join(combo_data_grts, design_better, by = c("sim"))
ggplot(data = design_better_full, aes(x = sim, y = coverage, colour = approach)) +
  geom_point() +
  coord_flip() +
  geom_hline(aes(yintercept = 0.95), alpha = 0.5)
```
